1 Report ASP20 Boost

### 2020-05-28 README.Rmd
clipped new tasks, clipped notes report

@@

```{r installation, eval = 3}
install.packages("devtools")
devtools::install_gitlab("asp20/asp20model", host = "gitlab.gwdg.de")
devtools::install_gitlab("asp20/asp20boost", host = "gitlab.gwdg.de")
library(asp20boost)
```

```{r}
model <- LocationScaleRegressionBoost$new(y ~ x, ~ x)
gradient_boost(model, 
              stepsize = 0.001, maxit = 1000,
              abstol = 0.001,
              verbose = FALSE)
plot(x, y)
lines(x,model$fitted_location)
#Todo do create similar graphic
curve(x + 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)
curve(x - 1.96 * exp(x*model$gamma), -0.1, 1.1, add = TRUE)

>>>>

### until ~ mid June

* extend documentation of R6-Class
  + inherit documentation from Hannes
  + add own extensions
  + both can be done via roxygen (see Wickham R-PAckages chp5)

* maybe move component-selection mechanism from active field in R6-Class to gradient_boost-function
  + intuition tells me R6-Class is not the right place to do central calculations of the algorithm
  + maybe create new helper function component_selection() which gradien_boost() can call

@@

```{r installation, eval = 3}
#install.packages("devtools")
#This throws an error for asp20boost
#devtools::install_gitlab("asp20/asp20model", host = "gitlab.gwdg.de")
#devtools::install_gitlab("asp20/asp20boost", host = "gitlab.gwdg.de")

model$gamma
```

```{r fig.width = 11, echo=FALSE}
# library(asp20boost)
# model <- LocationScaleRegressionBoost$new(y ~ x, ~ x)
# gradient_boost(model, 
#               stepsize = 0.001, maxit = 10000,
#               abstol = 0.001,
#               verbose = FALSE)
# 
# 
# 
# plot(x, y)
# lines(x,model$fitted_location)
# #For a 95% confidence interval, the value c = 1.96 is agood approximation
# curve(x + 1.96 * exp(model$gamma[1]+model$gamma[2]*x), -0.1, 1.1, add = TRUE)
# curve(x - 1.96 * exp(model$gamma[1]+model$gamma[2]*x), -0.1, 1.1, add = TRUE)

### 2020-05-28 Reports/1_REPORT.Rmd
add my notes 1_report
clipped new tasks, clipped notes report

@@

## Johannes is *gzus*.

@@

@@

>>>>

JS: Performance Needs to be checked and maybe more outputs - messages?
Starting point of Beta and Gamma?

L:

* user-friendliness: allow for convenient input of model, possibly as data.frame
* stability: trying to implement automated testing (unit tests)
* performance: 
  + custom step size for Beta needed, otherwise slow --> improve
  + move ProjectionMatrix Calculation to initializalisation to enhance efficiency

@@

## Johannes is *gzus* ^{2}.

L: implementation designs r6-Class "LocScRegBoost"

* moved calculation of central calculation matrices in boosting algorithm to initializer of R6-Class via super-command
* component-selection implemented inside R6-Class via additional active-fields
  + mechanism: calculation of n loss-function-values (n = #gamma-parameters = #beta-parameters), then compare to loss-functions of last iteration and choose highest loss-improvement
  + calculation does NOT work via derivatives as Kneib suggested, but by Hannes' deviance-residuals

@@

JS : Can this model be used to mathematically evaluate outliers, for example in the Munich rent data set -> use it to identify cheap apartments

L:

* How does cross-validation work in order to optimize stopping?
  + This connects to other applications of boosters such as variable selection. Variable selection is especially viable since component-wise boosting is already implemented
*	Is it possible to optimize the learning rate?

@@

L: Already implemented

* boosting for multidimensional (>2) beta or gamma 
* component-wise boosting

L: Ideas for further functionality

* better user-friendliness - allow inputs like my_model <- gradient_boost(formula, data = mtcars)
  + allow for model creation via dataframe-input
  + this may reduce errors due to unexpected inputs
* illustrate functions of package with real dataframe (= Vignette)
*	Visualization of results via connecting to plot team
*	functionality: predict 
*	Include model diagnostics

### 2020-05-28 Reports/1_REPORT.tex
clipped new tasks, clipped notes report

\title{1 Report ASP20 Boost}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{First Report}
\author{Johannes Strauß \and Levin Wiebelt \and Sebastian Aristizabal}
\date{27 Mai 2020}

@@

@@

\hypertarget{johannes-is-gzus.}{%
\section{\texorpdfstring{Johannes is
\emph{gzus}.}{Johannes is gzus.}}\label{johannes-is-gzus.}}

@@

@@

>>>>

\title{1 Report ASP20 Boost}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{First Report}
\author{Johannes Strauß \and Levin Wiebelt \and Sebastian Aristizabal}
\date{28 Mai 2020}

@@

JS: Performance Needs to be checked and maybe more outputs - messages?
Starting point of Beta and Gamma?

L:

\begin{itemize}
\tightlist
\item
  user-friendliness: allow for convenient input of model, possibly as
  data.frame
\item
  stability: trying to implement automated testing (unit tests)
\item
  performance:

  \begin{itemize}
  \tightlist
  \item
    custom step size for Beta needed, otherwise slow --\textgreater{}
    improve
  \item
    move ProjectionMatrix Calculation to initializalisation to enhance
    efficiency
  \end{itemize}
\end{itemize}

@@

\hypertarget{johannes-is-gzus-2.}{%
\section{\texorpdfstring{Johannes is \emph{gzus}
\^{}\{2\}.}{Johannes is gzus \^{}\{2\}.}}\label{johannes-is-gzus-2.}}

L: implementation designs r6-Class ``LocScRegBoost''

\begin{itemize}
\tightlist
\item
  moved calculation of central calculation matrices in boosting
  algorithm to initializer of R6-Class via super-command
\item
  component-selection implemented inside R6-Class via additional
  active-fields

  \begin{itemize}
  \tightlist
  \item
    mechanism: calculation of n loss-function-values (n =
    \#gamma-parameters = \#beta-parameters), then compare to
    loss-functions of last iteration and choose highest loss-improvement
  \item
    calculation does NOT work via derivatives as Kneib suggested, but by
    Hannes' deviance-residuals
  \end{itemize}
\end{itemize}

@@

JS : Can this model be used to mathematically evaluate outliers, for
example in the Munich rent data set -\textgreater{} use it to identify
cheap apartments

L:

\begin{itemize}
\tightlist
\item
  How does cross-validation work in order to optimize stopping?

  \begin{itemize}
  \tightlist
  \item
    This connects to other applications of boosters such as variable
    selection. Variable selection is especially viable since
    component-wise boosting is already implemented
  \end{itemize}
\item
  Is it possible to optimize the learning rate?
\end{itemize}

@@

L: Already implemented

\begin{itemize}
\tightlist
\item
  boosting for multidimensional (\textgreater2) beta or gamma
\item
  component-wise boosting
\end{itemize}

L: Ideas for further functionality

\begin{itemize}
\tightlist
\item
  better user-friendliness - allow inputs like my\_model \textless-
  gradient\_boost(formula, data = mtcars)

  \begin{itemize}
  \tightlist
  \item
    allow for model creation via dataframe-input
  \item
    this may reduce errors due to unexpected inputs
  \end{itemize}
\item
  illustrate functions of package with real dataframe (= Vignette)
\item
  Visualization of results via connecting to plot team
\item
  functionality: predict
\item
  Include model diagnostics
\end{itemize}
